\documentclass{article}
\begin{document}

\begin{small}\center   \textbf{               NJAKO SAMUEL             15/U/1010              215000346.}\end{small}

\begin{large}\textbf{A REPORT ABOUT HOTEL OPERATIONS IN UGANDA.}\end{large}

\section{Introduction.}
{Hotels in Uganda are changing and will continue to change. As a result, the techniques of
management of modern hotels must adapt to changing circumstances. This requires a system that will help to simplify the booking process while saving time and money, so that hotel managers could focus on what matters most: improving the guests’ experience. 
}
\section{Background to the problem.}
{Hotel operators usually find it a demanding experience to operate hotel business and they usually find themselves on their feet. The question is why spend so much time on tedious tasks such as training employees and manually calculating monthly sales. Worst of all, do they have to be present at the front desk all the time to ensure everything was running smoothly? The answer is a No
Hotel Studio was coded by a Team of experienced Lasahara Systems software developers to meet the existent gap in electronic data management within the hospitality industry. However their software has limited features like user friendliness, secure login and easy backup. Since our local systems lack the full package of needed deliverables there is a need to address this issue and adapt what other systems like hotel executive have. Hotel Executive is packed full of features to increase occupancy rates, generate more revenue and make every part of your hotel run smoothly - from reservations to reception, back office to housekeeping, restaurant and bar.
}
\section{Problem statement.}
{The problem this report will address is to improve hotel management experience. Using convention methods such as pen and paper, spreadsheet, or offline software, you are more prone to issues that will consume your time and money. Using a hotel management system is like having an employee by your side to manage, organize, and secure your hotel information, but at a fraction of the price.

Arka Uganda has designed systems that help in hotel management from booking and reservation, in-room entertainment, accountability, operations management; hotel services to daily reports of all the activities happening in a hotel but with almost one or two companies in business it is so expensive to acquire such systems therefore there is a need to curb the expenses for hotel managers and operators needing another hotel management system.
The hotel operator and user should therefore expect an easy-to-use system for dealing with enquiries, bookings, guest information, tasks and billing.
}
\section{Solutions to the problem.}
{An online hotel management system can be developed in order to solve the above problems. Such a system must be user friendly such that it can be conveniently used by hotel customers. 
}
\section{Benefits of the online hotel management system.}
{ The online hotel management system simplifies the booking process while saving time and money,
 provides secure online backup.
 This system also enables business owners to manage their businesses with ease and simplicity and
 carryout basic invoicing features. The system allows automatic update a customer’s details and 
provides remote online access.
}
\section{Research Scope.}
{The research scope is limited to hotels in major towns in Uganda because there is a need to address the existing gap in the management of electronic data in the hospitality industry.}
\section{Research Significance.}
{This study is important since it helps hotel owners to manage their hotels with a lot of ease and simplicity by providing a platform for training the employees at half the price
This study is also important because it improves customer experiences by providing them with important updates on the latest versions of release of the software.
}
\section{Conclusion.}
{This primitive hotel management system can be changed to adopt a better way of conducting services in hotels. An online hotel management system would work better than the current manual system. This system can reduce on delays and other difficulties faced by the hotels.
I would advise hotels to adopt the online system.
}
\end{document}